Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-31 cvpr2018.tex
10th

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions. We show a fully end-to-end trainable network that can generate up to $512^2$ resolution.
Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations to be compositional of multi-scale images. We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions with symmetric convolutional blocks. We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e. image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution. 
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Generating photographic high-resolution image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}. However, insufficient methods have been successfully developed to address this task due to its particular challenges. Text-to-image synthesis can be viewed as an special variation of conventional generative models, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.  Differently, the embedding space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve the principal concept of descriptions generally but also preserve the fine-grained descriptive details in image pixels.

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually can barely generate vivid object details.
Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images. This method needs two-stage training to achieve the goal. Later on, Dong \etal \cite{dong2017semantic} 
bypasses the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128{\times}128$) image conditioned on a targeting semantic description. Unfortunately, its high resolution synthesis ability is still unclear. 
At present, how to train from the low-dimensional embedding to synthesize high resolution (e.g. $256^2$) and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical observations for this challenges using GANs, particularly for text-to-image synthesis. The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. The second is that huge pixel space in high resolution images \cite{han2017stackgan}. 
An effective regularization to reduce the variances in generators is critical \cite{huang2016stacked}. 
Moreover, keeping semantic consistency and diversity in generated images needs more specialized designs in generators to better make use of gradients from discriminators. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these outlined problems, in this paper, we propose a novel method that can directly generate high resolution and semantic consistent images trained in a fully end-to-end manner. The contributions are described follows.

To tackle the problem of space leap from text and images, our method leverages the hierarchical representations of convolutional layers through a deeply-nested layer constraint, which is motivated by two insights. 
First,

First, we expect feature maps at different layers are disentangled RGB image space, which can linearly represent targeting images at corresponding resolutions. And second, we maximize the implicit effectiveness of feature representations with additional supervision.
We introduce ``accompanying'' hierarchically-nested adversarial objective at intermediate layers to encourage a more effective generators. 
To better cooperate with discriminators, we present an network structure design than can uses gradient more effectively.

To better use image and text information in GAN training, 
\textcolor{red}{we enforce discriminators at different resolutions can simultaneously differentiate real and fake image-text pairs, images, and patches.}
This multi-purpose conditional strategy is mutually beneficial to encourage them only focus on respect duties. It is a regularization to limit the discriminators to use unexpected information to make decision.

We have validated our proposed method on three datasets, i.e. CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\section{Related Work}
Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative} introduce the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a pretrained ImageNet CNN \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.

@@

To synthesize high resolution image, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}. Karras \cite{} train progressive GAN to scale up to high resolution. Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which enables end-to-end high resolution image synthesis.

@@

\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU \cite{} (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension. There two branches are added on top of it for multi-purpose discriminator design (see next section) . One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake. Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding). Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results. Finally, a $4{\times}4$ conv layer produces a 2-d vector.

@@

We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation. It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}. Lower score indicates higher variance.

@@

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.477\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
							 		&	 CUB		&	Oxford  & COCO		     \\ \hline
			GAN-INT-CLS 	&	$2.88{\pm}.04$		& 	$2.66{\pm}.03$		& $7.88{\pm}.07$	 \\
			GAWWN 	  &		$3.60{\pm}.07$		&     -      &          - \\ 
			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03$		\\ 
		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
			TAC-GAN	 &	-		&		$\bm{3.45{\pm}.05}$		& -	\\	
			StackGAN++     &		$3.84{\pm}.06$	&	 -			&  -	\\  \hline
			HDGAN 		&	$\bm{4.01{\pm}.06}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
		\end{tabularx} \vspace{-.4cm}
	\end{center}
	\caption{The inception-score evaluation on three datasets. The higher score reflects more meaningful synthetic images and higher diversity. The proposed HDGAN outperforms others significantly.} \label{table:score}
\end{table}

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.42\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			Scale 						& StackGAN & HDGAN & HR Test					\\ 				\hline
            $64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ &  ${3.46{\pm}.04}$	\\
           $128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$	& ${3.45{\pm}.04}$	\\
           $256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ & ${3.46{\pm}.04}$ \\ \hline
		\end{tabularx}
	\end{center} \vspace{-.4cm}
	\caption{Scale accuracy \textcolor{red}{changing to figure is better}.} \label{table:deep-nest}
\end{table}

\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on CUB} \label{fig:vis-cub}
\end{figure}
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on Oxford} \label{fig:vis-oxford}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=0.4\textwidth]{figure/ms_ssmi.pdf}
	\caption{Class-wise MS-SSMI evaluation compared to StackGAN.  Note that lower score indicates higher inter-class invariance. The points below the equality line represent classes our HDGAN wins. } \label{fig:msssmi}
\end{figure}
%
\subsection{Comparative Results}
We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, and StackGAN \cite{han2017stackgan} and also its improved version StackGAN++\footnote{This comes from a recently released pre-print from the author of StackGAN we just noticed, which outperforms StackGAN. Similarly with our HDGAN, it now can train $64{-}256$ directly. Each generator still take images from the bottom generator and supervised by a discriminator. Differently, our network is more like a simple Vanilla network (or a pure inverse ImageNet CNN).}.

StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution. We show that our method can generates images up to $512{\times}512$.

@@

@@

\subsection{Design principles}
Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
At the same time, it also shows the difficulty (impossibility) of directly training a vanilla $256{\times}256$ GAN, which fails to generate meaningful images. 
We test this extreme case using our method by removing all nested supervisions (the first row of Table \ref{table:deep-nest}). 
Our method actually can still generate fairly good. Figure \ref{fig:vallina-res} shows the qualitatively results. This strongly proves the effectiveness of our designs in generators and discriminator losses.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel and effective method to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions. We show a fully end-to-end trainable network that can generate high resolution images (e.g. $512^2$).
Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations and capture the complex image statistics. We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions. \textcolor{red}{We present a functional generative adversarial networks (GANs) training strategy} to encourage more effective multimodal (i.e. image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution. 
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Generating photographic image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}. However, insufficient methods have been successfully developed to address this task due to its particular challenges. Text-to-image synthesis can be viewed as an special variation of conventional generative models, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.  Differently, the embedding space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions generally but also preserve fine-grained descriptive details in image pixels.

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} is th first to address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually can barely generate vivid object details.
Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images. This method needs two-stage training to achieve the goal. Later on, Dong \etal \cite{dong2017semantic} 
bypasses the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128{\times}128$) image conditioned on a targeting semantic description. Unfortunately, its high resolution synthesis ability is still unclear. 
At present, how to train from the low-dimensional text space to synthesize high resolution and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical reasons for this challenges using GANs to deal with text-to-image synthesis. The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. The second is that huge pixel space in high resolution images \cite{han2017stackgan}. 
An effective regularization to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as preserve semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution. The contributions are described follows.

Our generator is a simple Vanilla GAN, without needing any inside text conditioning \cite{han2017stackgan} or image label supervision \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high resolution image space, our insight is to leverage hierarchical representations with additional implicit constraints to reduce training instability. 
We introduce ``accompanying'' hierarchically-nested adversarial objective at intermediate layers to generate multi-scale images.  
And we present an generator network structure design than can uses gradients from multi-scale nested discriminators more effectively.

To better make use of image and text information in GAN training, 
\textcolor{red}{we enforce discriminators at different resolutions can simultaneously differentiate real and fake image-text pairs, images, and patches.}
This multi-purpose conditional adversary is mutually beneficial to encourage each only focuses on respect duties. 
%It is a regularization to limit the discriminators to use unexpected information to make decision. 
We validate our proposed method on three datasets, i.e. CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale COCO datasets \cite{lin2014microsoft}. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\section{Related Work}
We discussed related methods as well as clarify the novelty of our method.

Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative} introduce a method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a pretrained ImageNet CNN \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.

@@

To synthesize high resolution images, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}. Recently, Karras \cite{} show a progressive training of GANs to enable high resolution image generation. Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which enables end-to-end high resolution image synthesis.

@@

\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension. There two branches are added on top of it for multi-purpose discriminator design (see next section) . One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake. Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding). Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results. Finally, a $4{\times}4$ conv layer produces a 2-d vector.

@@

We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further image quality validation. It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}. Lower score indicates higher variance.

@@

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.477\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
							 		&	 CUB		&	Oxford  & COCO		     \\ \hline
			GAN-INT-CLS 	&	$2.88{\pm}.04$		& 	$2.66{\pm}.03$		& $7.88{\pm}.07$	 \\
			GAWWN 	  &		$3.60{\pm}.07$		&     -      &          - \\ 
			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03$		\\ 
		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
			StackGAN++     &		$3.84{\pm}.06$	&	 -			&  -	\\  
			TAC-GAN	 &	-		&		$3.45{\pm}.05$		& -	\\	\hline

			HDGAN 		&	$\bm{4.01{\pm}.06}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
		\end{tabularx} \vspace{-.4cm}
	\end{center}
	\caption{The inception-score evaluation on three datasets. The higher score reflects more meaningful synthetic images and higher diversity. The proposed HDGAN outperforms others significantly.} \label{table:score}
\end{table}

%\begin{table}[t] % retrieval
%	\begin{center}
%		\begin{tabularx}{.42\textwidth}{c|ccc}
%			\specialrule{1.5pt}{0pt}{0pt}  
%			Scale 						& StackGAN & HDGAN & HR Test					\\ 				\hline
%            $64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ &  ${3.46{\pm}.04}$	\\
%           $128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$	& ${3.45{\pm}.04}$	\\
%           $256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ & ${3.46{\pm}.04}$ \\ \hline
%		\end{tabularx}
%	\end{center} \vspace{-.4cm}
%	\caption{Scale accuracy \textcolor{red}{changing to figure is better}.} \label{table:multiscales}
%\end{table}
\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.32\textwidth}{c|cc}
			\specialrule{1.5pt}{0pt}{0pt}  
			Scale 						& StackGAN & HDGAN 					\\ 				\hline
			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ \\
			$128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$		\\
			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ \\ \hline
		\end{tabularx}
	\end{center} \vspace{-.4cm}
	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:multiscales}
\end{table}
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on CUB} \label{fig:vis-cub}
\end{figure}
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on Oxford} \label{fig:vis-oxford}
\end{figure}

\begin{table}[t] % retrieval
	\begin{minipage}[b]{0.50\linewidth}
		%\centering
		\includegraphics[width=0.99\textwidth,height=0.7\textwidth]{figure/ms_ssmi.pdf}
		\vspace{-1.8cm}
	\end{minipage} %\hfill
	\begin{minipage}[b]{0.49\linewidth}
		\begin{tabularx}{.9\textwidth}{c|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			Method   &  MS-SSMI \\ \hline
			StackGAN &   0.234   \\ 
			Prog.GAN &   0.225    \\ \hline
			HDGAN    &   \textbf{0.215}    \\
		\end{tabularx}
	\end{minipage}
	\vspace{0.2cm}
	\caption{Left: Class-wise MS-SSMI evaluation. Lower score indicates higher intraclass invariance. The points below the equality line represent classes our HDGAN wins. Right: Overall (no class-wise) score evaluation.} \label{fig:msssmi}
\end{table}

\subsection{Comparative Results}
To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{}, and Progressive GAN \cite{} \footnote{Note that StackGAN++ and Prog.GAN are two very recent released pre-prints we noticed before submission. We acknowledge them as they also target at generating high resolution images, in spite of their differences in motivations and network and training designs from ours. }

% Similarly with our HDGAN, it now can train $64{-}256$ directly. Each generator still take images from the bottom generator and supervised by a discriminator. Differently, our network is more like a simple Vanilla network (or a pure inverse ImageNet CNN).}.

%StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution. We show that our method can generates images up to $512{\times}512$.

@@

Table \ref{table:multiscales} quantitatively compares the the multi-resolution inception score. Our results are from the side outputs of a single model. Usually higher resolution images gives rise to better inception score since they contain details. As can be observed, our $64^2$ images outperforms $128^2$ images of StackGAN and our $128^2$ images outperforms $256^2$ images of StackGAN substantially.

Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and ProgressiveGAN. StackGAN and our HDGAN use the semantic text as input so the generated images retain class information. We compare the score with StackGAN using the provided pretrained model). We randomly sample ${~}20,000$ image pairs (400 per class) and show the class-wise score in the left figure. HDGAN shows better performance in majority of classes and also has lower inter-class standard divition (0.023 vs. 0.032).
Prog.GAN takes noises rather than text. Since MS-SSMI evaluates the image quality without text or class involvement, we can compare with it. Following the procedure of Prog.GAN, we randomly sample ${~}10,000$ image pairs for each comparing method (For Prog.GAN, we use generated $256^2$ images provided by the author) and show the results in the right table. Our method outperforms both StackGAN and Prog.GAN.

@@

\subsection{Design principles}
Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
At the same time, it also shows the difficulty (impossibility) of directly training a vanilla $256{\times}256$ GAN, which fails to generate meaningful images. 
We test this extreme case using our method by removing all nested supervisions (the first row of Table \ref{table:deep-nest}). Our method still generates fairly good results. Figure \ref{fig:vallina-res} shows the qualitatively results. This strongly proves the effectiveness of our designs in generators and discriminator losses.
